\chapter{Cite As}
The main reference for Serenity is published as:\\
\\
J. P. Unsleber, T. Dresselhaus, K. Klahr, D. Schnieders, M. B{\"o}ckers, D. Barton and J. Neugebauer, ''Serenity: A Subsystem Quantum Chemistry Program``,
 \textit{J. Comput. Chem.}, \textbf{39}, 788--798, (2018).\\
\\
The BibTeX code would thus be:
\begin{lstlisting}
@article{serenity_pub,
  title = {Serenity: A Subsystem Quantum Chemistry Program},
  author = {Jan P. Unsleber and Thomas Dresselhaus and Kevin
            Klahr and David Schnieders and Michael B{"o}ckers
            and Dennis Barton and Johannes Neugebauer},
  journal = {J. Comput. Chem.},
  volume = {39},
  pages = {788--798},
  year = {2018}
}
\end{lstlisting}
Please also cite the second publication:\\
\\
N. Niemeyer, P. Eschenbach, M. Bensberg, J. T{\"o}lle, L. Hellmann, L. Lampe, A. Massolle, A. Rikus, D. Schnieders, J. P. Unsleber, and J. Neugebauer,
''The subsystem quantum chemistry program Serenity'',
\textit{Wiley Interdiscip. Rev. Comput. Mol. Sci.}, \textbf{13}, e1647, (2023).\\
\\
The BibTeX code would thus be:  
\begin{lstlisting}
@article{serenity_update,  
title={{The Subsystem Quantum Chemistry Program Serenity}},  
author={Niemeyer, Niklas and Eschenbach, Patrick and Bensberg, Moritz
        and T{\"o}lle, Johannes and Hellmann, Lars and Lampe, Lukas 
        and Massolle, Anja and Rikus, Anton and Schnieders, David 
        and Unsleber, Jan P and Neugebauer, Johannes},  
journal={Wiley Interdiscip. Rev. Comput. Mol. Sci.},  
volume={13},  
pages={e1647},  
year={2023},  
publisher={Wiley Online Library}
}
\end{lstlisting}
In order to allow others to reproduce your data and to give credit to all recent developers,
please also reference the version of Serenity used by citing the correct code reference
generated on Zenodo. The following DOI will always link to the newest version of the code:\\
\\ 
\url{https://doi.org/10.5281/zenodo.4017420}\\
\\
For specific versions, please use the appropriate DOI.\\
\\
Serenity relies on a few external libraries. Please cite Libint: \cite{Libint2.7.0}\\
\\
Libint: A library for the evaluation of molecular integrals of many-body operators  over Gaussian functions, v2.7.0-beta6, Edward F. Valeev, http://libint.valeyev.net/ \\
\\
BibTeX:
\begin{lstlisting}
  @misc{valeev2020libint,
  title={{Libint: A library for the evaluation of molecular integrals of 
          many-body operators over Gaussian functions}},
  author={Valeev, Edward F and Fermann, JT},
  howpublished={https://github.com/evaleev/libint},
  year={2020},
  note={version 2.7.0-beta6}
}
\end{lstlisting}
In case density functionals (for exchange-correlation or kinetic energy) are used, depending on the settings when compiling, please cite either Libxc \cite{Libxc} or XCFun \cite{XCFun2.0.2}.\\
\\
Libxc (6.1.0): S. Lehtola, C. Steigemann, M. J.T. Oliveira, and M. A.L. Marques. SoftwareX 7, 1-5 (2018). DOI: 10.1016/j.softx.2017.11.002\\
\\
BibTeX:
\begin{lstlisting}
  @article{lehtola2018recent,
  title={{Recent developments in libxc - A comprehensive library of functionals
        for density functional theory}},
  author={Lehtola, Susi and Steigemann, Conrad and Oliveira, Micael JT
          and Marques, Miguel AL},
  journal={SoftwareX},
  volume={7},
  pages={1--5},
  year={2018},
  publisher={Elsevier}
}
\end{lstlisting}
XCFun (v2.0.2):  Ekström, U. (2020). XCFun: A library of exchange-correlation functionals with  arbitrary-order derivatives. Zenodo. https://doi.org/10.5281/zenodo.3946698  \\
\\
BibTeX:
\begin{lstlisting}
  @software{ekstrom_2020_3946698,
  author       = {Ekstr{\"o}m, Ulf},
  title        = {{XCFun: A library of exchange-correlation 
                   functionals with arbitrary-order derivatives}},
  year         = 2020,
  publisher    = {Zenodo},
  version      = {v2.0.2},
  doi          = {10.5281/zenodo.3946698},
  url          = {https://doi.org/10.5281/zenodo.3946698}
  note         = {DOI: 10.5281/zenodo.3946698}
}
\end{lstlisting}
\newpage
\noindent Integrals over effective core potentials are provided by Libecpint \cite{Libecpint}.\\
Libecpint (1.0.7) :  R. A. Shaw, J. G. Hill, J. Chem. Phys. 147, 074108 (2017); doi: 10.1063/1.4986887\\
\\
BibTeX:
\begin{lstlisting}
@article{Libecpint,
author = {Shaw, Robert A. and Hill, J. Grant},
doi = {10.1063/1.4986887},
journal = {J. Chem. Phys.},
pages = {074108},
title = {{Prescreening and efficiency in the evaluation of integrals
 over ab initio effective core potentials}},
url = {http://aip.scitation.org/doi/10.1063/1.4986887},
volume = {147},
year = {2017}
}
\end{lstlisting}

Also, please include the scientific citations for the basis sets and density functionals you use. 

\chapter{License and Warranty}
This manual is part of \serenity. The full license file can be found in the appendix (Appendix~\ref{sec:lgpl})\\

\serenity is free software: you can redistribute it and/or modify it under
the terms of the GNU Lesser General Public License as published by the Free
Software Foundation, either version 3 of the License, or (at your option) any later version.
\serenity is distributed in the hope that it will be useful, but
WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY
or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.
You should have received a copy of the GNU Lesser General Public License along with
\serenity. If not, see http://www.gnu.org/licenses/.
