\subsection{Task: Active-Space Selection\label{sec:activeSpaceTask}}
This tasks performs an occupied orbital selection for the calculation of relative
energies along a reaction path. The atoms of all supersystems have to be identical
and ordered in the same way. If active and environment systems are provided via the
input, the results of the selection are saved in these systems. The charge, atoms, basis
set and spin may be changed. If no environment and/or active systems are provided
via the input, systems are constructed and written to disk with the names
supersystem name + ``\_act''/``\_env'' for active and environment system, respectively.
For information regarding the methodology we refer to the original publications~\cite{Bensberg2019a,Bensberg2020}.

\subsubsection{Example Input}
\begin{lstlisting}
  +task AS
    super reactant  
    super transition
    super product
    similarityLocThreshold 1e-2
    similarityKinEnergyThreshold 1e-2
    +loc
      locType IBO
    -loc
  -task
 \end{lstlisting}
\subsubsection{Basic Keywords}
\begin{description}
 \item [\texttt{Name}]\hfill \\
 Aliases for this task are \ttt{ACTIVESPACESELECTIONTASK}, \ttt{ACTIVESPACETASK} and \ttt{AS}.  
 \item [\texttt{Supersystems}]\hfill \\
 Accepts multiple supersystems (\ttt{super}) which are used for the orbital comparison.   
 \item [\texttt{ActiveSystems}]\hfill \\
 Accepts multiple active systems to which the active orbitals are parsed. The first
 active system is assumed to correspond to the first super system, the second to the second
 supersystem etc. 
 \item [\texttt{EnvironmentSystems}]\hfill \\
 Accepts multiple environment systems to which the environment orbitals are parsed. The first
 environment system is assumed to correspond to the first supersystem. 
 \item [\texttt{sub-blocks}]\hfill \\
 Orbital localization task (\ttt{loc}) settings are added via sub-blocks in the task settings.
 \item [\texttt{similarityLocThreshold}]\hfill \\
 The threshold for the comparison of partial charges. The default is \ttt{0.05}.
 \item [\texttt{similarityKinEnergyThreshold}]\hfill \\
 The threshold for the comparison of the orbital kinetic energy. The default is \ttt{0.05}.
 \item [\texttt{populationAlgorithm}]\hfill \\
 The algorithm used to calculate partial charges. The default are shell-wise intrinsic atomic orbital (IAO)
 charges (\ttt{IAOShell}). Other useful options are Mulliken charges (\ttt{MULLIKEN}) and atom-wise IAO
 charges (\ttt{IAO}).
 \item [\texttt{alignPiOrbitals}]\hfill \\
 Align the orbitals of all supersystems to the orbitals of the first supersystem (after localization). This
 is useful to avoid degenerate localization minima especially for $\pi$-systems. Default is \ttt{false}.
\end{description}
\subsubsection{Advanced Keywords}
\begin{description}
    \item [\texttt{localizationThreshold}]\hfill \\
    The atom-wise Mulliken population threshold for the assignment of atoms to the subsystems. This is done
    after the supersystem orbital set has been separated into active and environment orbitals. If the total
    population of the active orbitals on a given atoms exceeds this threshold it is assigned to the active
    system. The default is \ttt{0.8} au.
    \item [\texttt{load}]\hfill \\
    If true, the SCF procedure is skipped and the tasks tries to load the supersystem results. The default
    is \ttt{false}.
    \item [\texttt{usePiBias}]\hfill \\
    Use a selection threshold scaling based on the number of significant, orbital-wise partial charges for
    each orbital. This is used to reduce the over-selection of $\pi$-orbitals. The default is \ttt{false}.
    \item [\texttt{biasThreshold}]\hfill \\
    The threshold for the evaluation of the number of significant partial charges for. The default is
    \ttt{0.01}.
    \item [\texttt{biasAverage}]\hfill \\
    The averaging-parameter for the threshold scaling used for \ttt{usePiBias true}.
    The default is \ttt{12.0}.
    \item [\texttt{skipLocalization}]\hfill \\
    If \ttt{true}, the localization step is skipped. This can be useful if the orbitals were already
    localized. The default is \ttt{false}.
 \end{description}
