\subsection{Task: Coupled Cluster\label{sec:coupledClusterTask}}
This task performs coupled cluster calculations, possibly using canonical and local coupled cluster.
Additionally, this task also performs embedded coupled cluster calculations. Effects of an optional
PCM are taken only into account on the level of the orbitals/Fock matrix.

\subsubsection{Example Input}
\textbf{Canonical coupled cluster:}
\begin{lstlisting}
 +task CC
   system water
   level CCSD
 -task
\end{lstlisting}
\textbf{Local coupled cluster:}

{\color{red}IMPORTANT: } The orbital localization step for local coupled cluster is not carried out
within this task! Please make sure that the orbitals have been localized before using the local
correlation version of this task (see Sec.~\ref{task:localization}).
\begin{lstlisting}
 +task CC
   system water
   level DLPNO-CCSD
   +lc
     pno_settings tight
   -lc
 -task
\end{lstlisting}
\subsubsection{Basic Keywords}
\begin{description}
 \item [\texttt{name}]\hfill \\
   Aliases for this task are \ttt{CoupledClusterTask} and \ttt{CC}.
 \item [\texttt{activeSystems}]\hfill \\
   Accepts a single active system that will be used in the actual coupled cluster calculation.
 \item [\texttt{environmentSystems}]\hfill \\
   Accepts multiple environment systems that are used in embedded coupled cluster calculations.
 \item [\texttt{sub-blocks}]\hfill \\
   The embedding (\ttt{emb}), local correlation (\ttt{lc}) and PCM (\ttt{pcm}) settings are added via sub-blocks in the task settings.
   Prominent settings in the embedding block that are relevant for this task, and their defaults are:
   \ttt{naddXCFunc=BP86}, \ttt{embeddingMode=LEVELSHIFT}.
   Similarly, \ttt{pnoSettings=NORMAL} is a commonly changed default in the local correlation settings.
 \item [\texttt{level}]\hfill \\
   The type of coupled cluster calculation to perform. By default a (canonical) \ttt{CCSD} calculation is performed
   Alternatively canonical \ttt{CCSD(T)} and local \ttt{DLPNO-CCSD}, \ttt{DLPNO-CCSD(T0)} calculations can be
   requested with this keyword.
 \item [\texttt{maxCycles}]\hfill \\
   The maximum number of cycles allowed until convergence is expected by the coupled cluster iterations.
   By default \ttt{100} cycles are allowed.
 \item [\texttt{normThreshold}]\hfill \\
   The threshold at which the coupled cluster iterations are considered converged. By default \ttt{1.0e-5}.
\end{description}
\subsubsection{Advanced Keywords}
\begin{description}
  \item [\texttt{writePairEnergies}]\hfill \\
  Write the pair energies to a file with name: systemName\_pairEnergies\_CCSD.dat. This only works for
  DLPNO-CCSD/DLPNO-CCSD(T0). By default \ttt{false}.
\end{description}
