\subsection{Task: Local Correlation}\label{task:localCorrelation}
This tasks performs a local correlation (DLPNO-coupled cluster or MP2) calculation. This task only
calls other tasks. It serves as an input helper. It calls the localization task
(see Section~\ref{task:localization}) and the MP2 (see Section~\ref{task: mp2}) or Coupled Cluster task
(see Section~\ref{sec:coupledClusterTask}).
\subsubsection{Example Input}
\begin{lstlisting}
 +task LC
   system water
   +lc
     method DLPNO-CCSD(T0)
   -lc
 -task
\end{lstlisting}
\subsubsection{Basic Keywords}
\begin{description}
 \item [\texttt{name}]\hfill \\
   Aliases for this task are \ttt{LOCALCORRELATIONTASK}, \ttt{LC}.
 \item [\texttt{activeSystems}]\hfill \\
   Accepts a single active system which will be used in the calculation.
 \item [\texttt{environmentSystems}]\hfill \\
   Accepts a list of environment systems that are included in the Fock operator.
 \item [\texttt{sub-blocks}]\hfill \\
  Embedding (\ttt{\hyperref[sec:scb:emb]{emb}}) settings, local correlation (\ttt{\hyperref[sec:scb:lc]{lc}}) settings and
  orbital localization task (\ttt{\hyperref[task:localization]{loc}}) settings are added via sub-blocks in the task settings.
  By default, \ttt{splitValenceAndCore = true} is set for the localization task settings.
\end{description}
\subsubsection{Advanced Keywords}
\begin{description}
  \item [\texttt{maxCycles}]\hfill \\
  The maximum number of cycles allowed until convergence is expected by the coupled cluster iterations.
  By default, 100 cycles are allowed.
  \item [\texttt{normThreshold}]\hfill \\
  The threshold at which the coupled cluster/MP2 iterations are considered converged. By default \ttt{1.0e-5}.
  \item [\texttt{writePairEnergies}]\hfill \\
  Write the pair energies to a file with name: systemName\_pairEnergies\_CCSD.dat or systemName\_pairEnergies\_MP2.dat
\end{description}
