\subsection{Task: MP2}\label{task: mp2}
\label{sec:MP2}
This task performs MP2 calculations for a given active system, probably using embedding or local correlation
settings. Effects of an optional PCM are taken only into account on the level of the orbitals/Fock matrix.

{\color{red}IMPORTANT:} The orbital localization step for local MP2 is not carried out
within this task! Please make sure that the orbitals have been localized before using the local
correlation version of this task (see Sec.~\ref{task:localization}).
\subsubsection{Example Input}
\begin{lstlisting}
+task MP2
  system acetone
  mp2Type RI
-task
\end{lstlisting}
\subsubsection{Basic Keywords}
\begin{description}
	\item [\texttt{name}]\hfill \\
	Aliases for this task are \ttt{MP2} and \ttt{MP2Task}.
	\item [\texttt{activeSystems}]\hfill \\
	Accepts a single active system for whose orbitals an MP2 correction is calculated.
	\item [\texttt{environmentSystems}]\hfill \\
	Accepts mutiple environment systems that are used in embedded calculations.
	\item [\texttt{sub-blocks}]\hfill \\
	The embedding (\ttt{emb}), local correlation (\ttt{lc}) and PCM (\ttt{pcm}) settings are added via sub-blocks in the task settings.
	Prominent settings in the embedding block that are relevant for this task, and their defaults are:
	\ttt{naddXCFunc=BP86}, \ttt{embeddingMode=LEVELSHIFT}.
	Similarly, \ttt{pnoSettings=NORMAL} is a commonly changed default in the local correlation settings.
	\item [\texttt{mp2Type}] \hfill \\ 
	MP2 type used. Full four center integral MP2 (\ttt{AO}), DF-MP2, using density fitting approach specified with \ttt{densfitCorr} in the system block (\ttt{DF}), local MP2 (\ttt{LOCAL}), Laplace-transform SOS-MP2 (\ttt{LT}). By default \ttt{DF}.
  \item[\texttt{maxResidual}]\hfill \\
	Convergence threshold for the local MP2 calculation. By default \ttt{1.0e-5}.
  \item[\texttt{sss}]\hfill \\
	Scaling parameter for same-spin contributions. By default \ttt{1.0}.
  \item[\texttt{oss}]\hfill \\
	Scaling parameter for opposite-spin contributions. By default \ttt{1.0}.
  \item[\texttt{ltconv}]\hfill \\
	Convergence parameter for the Laplace transformation if LT-SOS-MP2 is used. By default \ttt{1e-5}.
  \item[\texttt{maxCycles}]\hfill \\
  Maximum number of iterations before cancelling the amplitude optimization in local MP2. By default \ttt{100}.
  \item[\texttt{unrelaxedDensity}]\hfill \\
  If true, the unrelaxed MP2 density is calculated. By default \ttt{false}. 
\end{description}
\subsubsection{Advanced Keywords}
\begin{description}
  \item [\texttt{writePairEnergies}]\hfill \\
  Write the pair energies to a file with name: systemName\_pairEnergies\_MP2.dat.
  This only works for DLPNO-MP2.
\end{description}
