\subsection{Task: Read/Write Orbitals to/from Disk}

This task allows to read and write orbitals from and to (non)-Serenity output files.\newline
Reading orbitals:
\begin{itemize}
  \item The ASCII-format for Turbomole is supported up to g functions.
  \item The xml format for Molpro is supported up to g functions.
  \item Molcas orbitals may be read up to arbitrary angular momentum.
  \item Furthermore, the task may read orbital files from Serenity.
\end{itemize}
Writing orbitals:
\begin{itemize}
  \item The ASCII-format for Turbomole is supported up to g functions. If a non-standard energy convergence threshold is used in Turbomole, this has to be changed in the written files afterwards.
  \item Molden files are supported up to g functions. Supports both spherical and cartesian harmonics.
\end{itemize}
Note that Serenity does not account for symmetry. Hence, the orbitals must be defined without any symmetry.
\subsubsection{Example Input}
\begin{lstlisting}
 +task READ
  act water
  fileformat turbomole
  path path/to/a/directory/containing/a/turbomole/ascii-mo-file
 -task
\end{lstlisting}

\subsubsection{Basic Keywords}
\begin{description}
 \item [\texttt{name}]\hfill \\
  Aliases for this task are \ttt{OrbitalsIOTask}, \ttt{ReadOrbs}, \ttt{Read}, \ttt{WriteOrbs}, \ttt{Write} and \ttt{IO}.
 \item [\texttt{activeSystems}]\hfill \\
  The system to which the orbitals should be read.
 \item [\texttt{fileFormat}]\hfill \\
  The file format to be expected by the task. Currently supported are the Turbomole ASCII-MO file format (\ttt{TURBOMOLE})
  Molpro's xml format (\ttt{MOLPRO}), the native \textsc{Serenity} HDF5 file format (\ttt{Serenity}), the Molcas-HDF5 file
  format (\ttt{Molcas}) and the \ttt{MOLDEN} file format. By default \ttt{TURBOMOLE}.
 \item [\texttt{resetCoreOrbitals}]\hfill \\
  If \texttt{fileFormat = SERENITY} and \ttt{true}, the core orbitals are reset to the core orbitals tabulated for the geometry. Otherwise, the core orbital
  definition on disk is used. Note that this is always done for \texttt{fileFormat = TURBOMOLE}.
 \item [\texttt{path}]\hfill \\
  The path to the orbital files. Default is \ttt{"."}.
 \item [\texttt{replaceInFile}]\hfill \\
  If true, copies the original orbital file and replaces the coefficients in this file by Serenity's coefficients. (Only implemented for Molcas HDF5 files).
  By default \ttt{false}.
 \item [\texttt{write}]\hfill \\
  If true, a file will be written instead of being read. By default \ttt{false}.
\end{description}
