\subsection{Task: Top Down Static Embedding}\label{sec:tasks:TopDownStaticEmbedding}
This tasks runs a top-down embedding calculations without additional relaxation of the orbital subspaces after supersystem partitioning.

\subsubsection{Example Input}
\begin{lstlisting}
 +task TDSTATIC
  act waterA
  act waterB
  env waterC
  useQuasiRestrictedOrbitals true
  +emb
      naddXcFunc pbe
      embeddingMode fermi
  -emb
 -task
\end{lstlisting}

\subsubsection{Basic Keywords}
\begin{description}
    \item [\texttt{name}]\hfill \\
    Aliases for this task are \ttt{TDSTATIC}, \ttt{STATIC}, and \ttt{TOPDOWNSTATICEMBEDDINGTASK}.
    \item [\texttt{activeSystems}]\hfill \\
    Accepts multiple active systems.
    \item [\texttt{environmentSystems}]\hfill \\
    Accepts multiple environment systems.
    \item [\texttt{useQuasiRestrictedOrbitals}]\hfill \\
    If true, quasi restricted orbitals are generated und used for the subsystem partitioning.
    All orbital localization steps will be restricted to rotations within the quasi restricted orbital subspaces.
    \item[\texttt{sub-blocks}]\hfill \\
    Possible sub-blocks are the embedding (\ttt{emb} with \ttt{naddXCFunc=BP86} and \ttt{embeddingMode=FERMI}), the local correlation (\ttt{lc} with \ttt{pnoMethod=None}),
    the PCM (\ttt{pcm}) settings, the orbital localization settings (\ttt{loc} with \ttt{splitValenceAndCore=true}), the system splitting settings (\ttt{split}),
    and the system addition settings (\ttt{add}).

\end{description}
\subsubsection{Advanced Keywords}
\begin{description}
    \item [\texttt{maxCycles}]\hfill \\
    The maximum number of cycles allowed until convergence is expected by the coupled cluster iterations.
    By default, 100 cycles are allowed.
    \item [\texttt{normThreshold}]\hfill \\
    The threshold at which the coupled cluster/MP2 iterations are considered converged. By default \ttt{1.0e-5}.
    \item [\texttt{writePairEnergies}]\hfill \\
    Write the pair energies to a file with name: systemName\_pairEnergies\_CCSD.dat or systemName\_pairEnergies\_MP2.dat
\end{description}